\section*{TU Braunschweig Subject-Specific Qualifications}

\noindent
\textbf{Application for MSc. Data Science}

\begin{longtable}{p{5cm} p{8cm} c}
\toprule
\textbf{Category} & \textbf{Course Equivalent} & \textbf{CP (ECTS)} \\
\midrule
\multicolumn{3}{c}{\textbf{ Computer Science (92 ECTS)} } \\
\midrule

% Practical CS
\textbf{Programming} 
& \hyperref[cs155]{CSCE 155E - Computer Science I} & 6 \\
& \hyperref[cs235]{CSCE 235 - Introduction to Discrete Structures} & 6 \\
& \hyperref[cs251]{CSCE 251 - UNIX Programming} & 2 \\
& \hyperref[cs301]{CSCE 301 - Data Structures \& Algorithms} & 6 \\
& \hyperref[cs474]{CSCE 474 - Introduction to Data Mining} & 6 \\
& \hyperref[cs478]{CSCE 478 - Introduction to Machine Learning} & 6 \\

\midrule

\textbf{Software Engineering}
& \hyperref[cs361]{CSCE 361 - Software Engineering} & 6 \\
\textbf{and Database\footnote{CSCE 156 covers topics on relational databases and their design. CSCE 401H and CSCE 402H capstone sequence involves the application of a Graph Database Neo4j. Excerpt from the project can be found \hyperref[cs402_capstone]{here}.}}
& \hyperref[cs156]{CSCE 156 - Computer Science II} & 8 \\
& \hyperref[cs401]{CSCE 401H - Design Studio I} & 6 \\
& \hyperref[cs402]{CSCE 402H - Design Studio II} & 6 \\

\midrule

% Technical CS
\textbf{Distributed Systems} 
& \hyperref[cs231]{CSCE 231 - Computer Systems Engineering} & 8 \\
\textbf{and IT Security} 
& \hyperref[cs451]{CSCE 451 - Operating Systems} & 6 \\

\midrule

% Theoretical CS
\textbf{Theoretical} 
& \hyperref[cs322]{CSCE 322 - Programming Language Concepts} & 6 \\
\textbf{Computer Science}
& \hyperref[cs423]{CSCE 423 - Design \& Analysis of Algorithms} & 6 \\
& \hyperref[cs136]{COMPSCI 136 - Economics \& Computation (Algorithmic Game Theory)}\footnote{Credits earned at the Harvard Kenneth C. Griffin Graduate School of Arts and Sciences. See \hyperref[sec: notes on document]{notes on the document} for more details.} & 8 \\


\midrule
\multicolumn{3}{c}{\textbf{Mathematics (60 ECTS)}} \\
\midrule

% Analysis
\textbf{Analysis} 
& \hyperref[math106]{MAT 133 - Calculus \& Analytical Geometry I}\footnote{Credits transferred from INTI International College Penang, which is deemed equivalent to MATH106 at the University of Nebraska-Lincoln. See \hyperref[sec: notes on document]{notes on the document} for more details.} & 8 \\
& \hyperref[math107]{MAT 134 - Calculus \& Analytical Geometry II}\footnote{Credits transferred from INTI International College Penang, which is deemed equivalent to MATH107 at the University of Nebraska-Lincoln. See \hyperref[sec: notes on document]{notes on the document} for more details.} & 8 \\
& \hyperref[math208]{MATH 208 - Calculus III} & 8 \\
& \hyperref[math325]{MATH 325 - Elementary Analysis} & 6 \\

\midrule

% Linear Algebra
\textbf{Linear Algebra} 
& \hyperref[math314]{MATH 314 - Linear Algebra} & 6 \\
\textbf{Modern Algebra}
& \hyperref[math310]{MATH 310 - Introduction to Modern Algebra} & 6 \\
& \hyperref[math417]{MATH 417 - Group Theory} & 6 \\
\midrule

% Further Competences
\textbf{Applied Mathematics}
& \hyperref[math428]{MATH 428 - Introduction to Operations Research} & 6 \\
& \hyperref[math435]{MATH 435 - Math in the City (Mathematical Epidemiology)} & 6 \\
\midrule

\textbf{Statistics} 
& \hyperref[econ215]{ECON 215 - Statistics} & 6 \\
\textbf{and Data Science} 
& \hyperref[stat380]{STAT 380 - Statistics and Application} & 6 \\
& \hyperref[econ417]{ECON 417 - Introduction to Econometrics} & 6 \\
& \hyperref[econ409]{ECON 409 - Economic Data Visualization} & 6 \\
& \hyperref[scma350]{SCMA 350 - Business Data Analytics} & 6 \\

\bottomrule
\end{longtable}

% SECTION: PROFESSIONAL EQUIVALENCY
\noindent
\textbf{Professional Equivalency for Required Areas} \\
\noindent
\textit{Refer to the CV for detailed information.}

\vspace{0.5em}

\noindent \textbf{Databases \& Data Engineering} \\
Researcher (Lead Author), Berkman Klein Center (Harvard) \hfill Oct 2024 -- Jun 2025 \\
Database Developer Intern, Farm Credit Services of America \hfill Aug 2021 -- Aug 2022

\vspace{0.5em}

\noindent \textbf{IT Security \& Computer Networks} \\
Intelligent Solutions Engineer, Unified Communications \hfill Sep 2025 -- Present
